### 2019-09-27 conflog.tex
adds transport during the conference

\subsubsection{Getting to the Conference}
The primary location for all conference events is the Illini Union. This is also the primary hotel for conference attendees. The secondary hotel, Marriott TowneSuites is merely a five minute walk from the Union.

>>>>

\subsubsection{Getting to the Conference}
The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance. Thus we have budgeted to include transportation provided by Peoria Charter. We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations.
